\documentclass{resume}
% Heading and general Information
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Alark Patel}
\address{ 
\href{mailto:patelalark1@gmail.com}{patelalark1@gmail.com} \\ \href{https://www.linkedin.com/in/alark-patel/}{linkedin.com/in/alark-patel}\\
\href {https://github.com/AlarcPatel} {https://github.com/AlarcPatel}
}
\begin{document}

%	EDUCATION SECTION

\begin{rSection}{Education}
{\bf Rutgers University}  \hfill {\bf Spring 2021}\\
{\bf B.Sc in Computer Science}\\
{ \bf Relevant Courseworks}: {\bf Data Structures, Algorithms}, Data Science, {\bf Database management},\\
Internet Technology, Principles of Programming Languages 
\end{rSection}

% TECHNICAL STRENGTHS	
\begin{rSection}{EXPERIENCES}

%First point

\textbf{R\&D Team: Hackathon at Rutgers University} \hfill Spring 2019
 \begin{itemize}
    \itemsep -2pt {} 
     \item \text \textbf{Collaborated} with team members to discuss the issues prior to the {\bf app deployment  \&  performed manual testing} on application for multiple devices.
     \item Used Dart and  Flutter framework to make astonishing experience for both {\bf Android and IOS users.}
 \end{itemize}
 % Second Point
 
\textbf{Science Learning Center (Volunteer)} \hfill Fall 2018
 \begin{itemize}
    \itemsep -2pt {} 
     \item \text {\bf Instructed} students with plotting and graphing data into Excel to find error points using GLX.
     \item Helped Students with {\bf Calculus(I,II) \& Physics homework and problem sets.}
 \end{itemize}
\end{rSection} 

%	WORK EXPERIENCE SECTION

\begin{rSection}{Projects}
\textbf{Railway Registration System} \hfill Spring 2020
 \begin{itemize}
    \itemsep -3pt {} 
     \item {\bf Lead} a team of 5 to develop the simple user-friendly {\bf web application} which uses real world data from New Jersey Transit System.
    \item {\bf Functionalities} such as add, edit and delete train schedules, customer support,        admin portal and employee portal.
    \item {\bf Used MySQLfor back-end} and {\bf JSP/HTML/CSS for front-end.} 

 \end{itemize}
\textbf{Prediction Modeling} \hfill Spring 2019
 \begin{itemize}
    \itemsep -2pt {} 
     \item Predicted the Grade earnings from students performance with high accuracy of {\bf98.9\% } using {\bf random forest amongst the ANN, SVM and R-part.}
     \item {\bf Explored and Visualized} the data using r-studio, observed the trends and {\bf implemented appropriate function } for least MSE. 
 \end{itemize}
 
 \textbf{Polynomial Calculator} \hfill Fall 2018
 \begin{itemize}
    \itemsep -2pt {} 
     \item {\bf The calculator performs arithmetic operations} such as addition, subtraction,
           multiplication on for two distinct polynomial equations. 
     \item Used Linked List to increase the {\bf efficiency of the algorithm}, it also calculates the  {\bfx $^{nth}$ power} variable.
 
 \end{itemize}

\end{rSection} 

\begin{rSection}{SKILLS}

\begin{tabular}{ @{}  @{\hspace{6ex}} l }
{\bf Programming Languages}: \textbf{ Python3, Java,} My-SQL, HTML/CSS\\
Familiar Languages: {\bf C,} R, Prolog, Ocaml, dart\\
Tools: {\bf Git, Linux}, bash, Vim, Jupyter Notebooks  \\
{\bf Frameworks: Flask, Django,} Pandas, 
\end{tabular}\\
\end{rSection}

% Leadership and Activities
\begin{rSection}{Leadership \& Activities} 
\begin{itemize}
    \item \textbf{CS Mentor}: Helping underclassmen mentees with holistic {\bf mentoring} on academic and career development.
    \item  {\bf Member: Rutgers University Competitive Programming.} and FizzBuzz(Mock interview club).
\end{itemize}
\end{rSection}
\end{document}
